
\section{Results}
\subsection{Determination of the resonance points}
The resonance points can be taken from the resonance curves, which were drawn by the
XY-plotter. These are atteched in the appendix.
With the calibration of the x-axis every cm is linear propotional to 50\,mA, which is used for
the data of the table \ref{fig:Resonanzstelle} .
\newline
The values of the parallel orientation are placed in every first line of each frequency,
the values of the antiparallel orientation in the second.
\begin{table}
  \centering
  \caption{Distance and related currents of the resoncance points }
  \begin{tabular}{c c c c}
    \toprule
    {$\su{\nu_e}$\,/\,MHz}& $\su{x}\,/\,\mathrm{cm}$ & {I\,/\,$\mathrm{mA}$} & {B\,/\,$\su{\mu}$T} \\
    \midrule
     14,798 & 8,3 & 415 & 582 \\
            & 7,2 & 360 & 505 \\
     19,448 & 11,0 & 550 & 771 \\
            & 10,0 & 500 & 701 \\
     23,888 & 12,6 & 630 & 884 \\
            & 11,5 & 575 & 807 \\
     29,448 & 15,7 & 785 & 1101 \\
            & 14,5 & 725 & 1017 \\
    \bottomrule
    \label{fig:Resonanzstelle}
  \end{tabular}
\end{table}
\newline
The magnetic field is calculated with equation \ref{eqn:1}.

\subsection{Determinaton of the Landé g-factor and the earth's magnetic field}
The earths's magnetic field can be calculated with
\begin{equation*}
    B_{earth}=\frac{1}{2}(B_p-B_a).
\end{equation*}
In result the values of the magnetic field are listed in table \ref{fig:Erde}
\begin{table}
  \centering
  \caption{Values of the magnetic field}
  \begin{tabular}{c c}
    \toprule
    {$\su{\nu_e}$\,/\,MHz} & {$\su{B_{erd}}$\,/\,$\su{\mu}$T} \\
    \midrule
     14,798 & 38,5 \\
     19,448 & 35,0 \\
     23,888 & 38,5 \\
     29,448 & 42,0 \\
    \bottomrule
    \label{fig:Erde}
  \end{tabular}
\end{table}
\newline
The mean value, which can be estimated with
\begin{equation}
  \bar{x} = \frac{1}{n} \sum{x_n}
  \label{eqn:Mittelwert}
\end{equation}
and
\begin{equation}
\upsigma = \frac{1}{\sqrt{n}} \sqrt{\frac{\sum{(x_n - \bar{x})^2}}{n-1} },
\label{eqn:Standardabweichung}
\end{equation}
is
\begin{align*}
  \bar{B}_{earth} = 38,75\pm1,24.
\end{align*}
The Lande g-factor can be calculated with
\begin{equation*}
    g  = \frac{h\nu_e}{B\mu_b}.
\end{equation*}
In result the eight g-factors for each frequency and orientation are listed
in table \ref{fig:Lande}
\begin{table}
  \centering
  \caption{Values of the g-factor}
  \begin{tabular}{c c c}
    \toprule
    {$\su{\nu_e}$\,/\,MHz}& $\su{x}\,/\,\mathrm{cm}$ & {g} \\
    \midrule
     14,798 & 8,3 & 1,82 \\
            & 7,2 & 2,09 \\
     19,448 & 11,0 & 1,80 \\
            & 10,0 & 1,98 \\
     23,888 & 12,6 & 1,93 \\
            & 11,5 & 2,12 \\
     29,448 & 15,7 & 1,59 \\
            & 14,5 & 1,72 \\
    \bottomrule
    \label{fig:Lande}
  \end{tabular}
\end{table}
\newline
The mean value of the g-factor is calculated with \ref{eqn:Mittelwert} and \ref{eqn:Standardabweichung}.
It amounts of
\begin{align*}
    \bar{g} = 1,88\pm0,06.
\end{align*}

\newpage
\section{Discussion}
All of the results are presented and compared to their theoretical value in table \ref{fig:theo}.
\begin{table}
  \centering
  \caption{Comparison between measures and theoretical value}
  \begin{tabular}{c c c c}
    \toprule
     & $\text{Measures}$ & $\text{Theoretical value} $& $\text{Deviation in percent}$\\
    \midrule
     $\su{B_{earth}}$ & 38,75\pm1,24 $\su{\mu}$T & 44 \cite{1} $\su{\mu}$T & 11,93 \% \\
     g & 1,88\pm0,06 & 1,761 \cite{2} & 6,76 \% \\
    \bottomrule
    \label{fig:theo}
  \end{tabular}
\end{table}
\newline
Eventhough the deviation in percent is with 6,67\% for the g-factor and 11,93\% for the
earth's magnetic field small, there are some sources of error in the implentimantation aswell as in the analysis
of the resonance curves. The adjustment of the bridge voltage was imprecised because it was not possible
to regulate the voltage close to zero. At some point the resonance curve was hard to find and additionally
the drawing with the XY-plotter made the resonance point even more flatter. By analysing the curves by hand
it was, especially for the 23,888\,MHz frequency, difficult to get exact values of the coordinate paper.
\newline
Nevertheless the generated results are close to the theoretical values despite of some inaccuracies in the
implentimantation and analysis by hand.
